---
title: |
  Lecture title
date: |
  Subject  
  Week
author: |
  Me  
---

# Contents slide starts with a single \#

## Normal slides start with a double \#\#

- content goes here

## Columns

:::::::::::::: {.columns align="center"}
::: {.column width="0.5"}

left col

:::
::: {.column width="0.5"}

right col

:::
::::::::::::::

## Overprint

## Clipped images


## Code blocks

:::::::::::::: {.columns align="center"}
::: {.column width="0.33"}

\footnotesize

```{.anyclass}
put anything in the
class name and you
get grey
```

- it should match the text indent

:::
::: {.column width="0.33"}

\footnotesize

```{.anyclass .numberLines}
add .numberLines for
numbered lines
```


:::
::: {.column width="0.33"}

\footnotesize

```{.anyclass .numberLines}
work out bash/python
```


:::
::::::::::::::

## Alert blocks

:::::::::::::: {.columns align="center"}
::: {.column width="0.5"}

::: block

### Alerted block {.alert}

- alerted content

:::

- use the three colons to break out of the alertblock

:::

::: {.column width="0.5"}

### We also have unstyled H3 blocks

- this matches the layout of alert blocks
- but has no colour

\scriptsize
\setbeamerfont{block title}{size=\tiny}

### You need to use latex code to style the headers {.alert}

- use the contrast sparingly for highlights


:::
::::::::::::::

# Example algorithms

## Example algoriths

:::::::::::::: {.columns align="center"}
::: {.column width="0.5"}

<!-- alert looks good with \usepackage[lined,linesnumbered]{algorithm2e} -->
<!-- otherwise, use \usepackage[lined,linesnumbered,ruled,titlenotnumbered]{algorithm2e} -->

\scriptsize
\setbeamerfont{block title}{size=\footnotesize}


### {.alert}

\RestyleAlgo{algoruled}

\begin{algorithm}[H]  

\NoCaptionOfAlgo
\DontPrintSemicolon
\SetAlgoVlined
%\SetAlgoNoEnd

\caption{K-means $(D, k, \epsilon)$}

$t=0$\;
Randomly initialize $k$ centroids: $\mu_1^t, \mu_2^t, ..., \mu_k^t \in \mathbb{R}^d$ \;

\Repeat{$ \sum_{i=1}^{k}{\left\Vert \mu_i^t - \mu_i^{t-1} \right\Vert^2 \leq \epsilon}$}{
  $t \gets t + 1$ \;
  $C_j \gets \varnothing$ for all $j = 1, ..., k$ \;
  \tcp{Cluster assignment step}
  \ForEach{$x_j \in D$}{
    $j^* \gets \arg \min_i \left\{\left\Vert x_j - \mu_i^t \right\Vert^2 \right\}$
      \tcp*[r]{Assign $x_j$ to closest centroid}
    $C_{j^*} \gets C_{j^*} \cup \left\{x_j \right\}$ \;
    }
  \tcp{Centroid update step}
  \ForEach{$i=1 \text{ to } k$}{
    $ \mu_i^t \gets \frac{1}{\lvert C_i \rvert} \sum_{x_j \in C_i}{x_j}$
  }
}

\end{algorithm}

:::
::: {.column width="0.5"}

\scriptsize
\setbeamerfont{block title}{size=\footnotesize}

### {.alert}


\RestyleAlgo{algoruled}

\begin{procedure}[H]  

%\NoCaptionOfAlgo
\DontPrintSemicolon
%\SetAlgoVlined
\SetAlgoNoEnd

\caption{Dbscan(X, $\epsilon$, minpts)}

\SetKwFunction{GetNeighbours}{GetNeighbours} 

\ForEach{unvisited point $x \in X$}{
  mark $x$ as visited \;
  $N \gets \GetNeighbours{x, ε}$ \;
  \If{$\lvert N \rvert < minpts$}{
    mark $x$ as noise}
  \Else{
    $C \gets \left\{ x \right\}$ \;
    \ForEach{point $x' \in N$}{
      $N \gets N \setminus x'$ \;
      \If{$x'$ is not visited}{
        mark $x'$ as visited \;
        $N' \gets \GetNeighbours{x′, ε}$ \;
        \If{$\lvert N' \rvert \geq minpts$}{
          $N \gets N \cup N'$}}
      \If{$x'$ is not yet member of any cluster}{
        $C \gets C \cup \left\{ x' \right\}$}
    }}}


\end{procedure}

:::
::::::::::::::


## label equations

:::::::::::::: {.columns align="center"}
::: {.column width="0.5"}


\begin{alignat*}{3}
& \text{Non-negativity: } && d(a,b) && \geq 0 \\
& \text{Identity: } && d(a,a) && = 0 \\
& \text{Symmetry: } && d(a,b) && = d(b,a) \\
& \text{Triangle inequality: }  && d(a,c) && \leq d(a,b)+ d(b,c)
\end{alignat*}

:::
::: {.column width="0.5"}


\footnotesize\centering

Conditional probability:

\vspace{2ex}

$$
\tikzmarknode{A}{P(A \mid B)} = \frac{\tikzmarknode{B}{P(A \cap B)}}{\tikzmarknode{C}{P(B)}}
\begin{tikzpicture}[overlay, remember picture,shorten <=1mm,
                    nodes={inner sep=1pt, align=center, font=\tiny}]
\draw (A.south) ++ (0, -0.1) node[below, text=viridis1] {Probability of\\ A given B};
\draw (B.north)  ++ (0, 0.1) node[above, text=viridis5] {Probability of\\ A and B};
\draw (C.south)  ++ (0, -0.1) node[below, text=viridis5] {Probability of B};
\end{tikzpicture}
\vspace{3ex}
$$


:::
::::::::::::::

## tables

:::::::::::::: {.columns align="center"}
::: {.column width="0.5"}

It's safe to use markdown in the table cells, e.g. \textcolor{viridis5}{like this}.

```{r localglobal, results='asis'}
mytab = data.table::fread("data/trees.csv", header = TRUE)
pander::pandoc.table(
  mytab,
  split.tables = Inf,
  split.cells = Inf,
  style = "multiline",
  justify = "cc",
  keep.line.breaks= FALSE)
```


:::
::: {.column width="0.5"}


Suppress column headers

```{r treeseq, results='asis'}
mytab2 <- data.table::fread("data/treeseq.txt", header = FALSE)
names(mytab2) <- NULL
pander::pandoc.table(
  mytab2,
  split.tables = Inf,
  split.cells = Inf,
  style = "simple",
  justify = "cc",
  keep.line.breaks= FALSE)
```

:::
::::::::::::::
